CrypTool Script\footnote{ Background reading for the CrypTool program}\\ Mathematics and Cryptography

### 2003-06-13 script/en/chapters/numbertheory.tex
be updates

The best factorisation method known today is a further development of the
General Number Field Sieve (GNFS), which was originally devised to
factor only numbers of a special form (like Fermat numbers).  The
complexity of solving the factorisation problem with the GNFS is
asymptotically
$$
O(l) = e^{c \cdot (l \cdot \ln 2)^{1/3} \cdot  (\ln(l \cdot \ln(2))^{2/3} + o(l)}
$$
Please refer to: 
\vspace{-10pt}
\begin{itemize}{}
  \item A. Lenstra, H. Lenstra:  
          {\em The development of the Number Field Sieve} 
          \cite{Lenstra1993}.
  \item   Robert D. Silverman:  
          {\em A Cost-Based Security Analysis of Symmetric and Asymmetric
          Key Lengths} 
          \cite{Silverman2000}.
\end{itemize}

@@

\item In 1999 a 155-digit module (512 bit) was factored with an implementation
      of the General Number Field Sieve algorithm (GNFS), developed by Buhler,
      Lenstra and Pomerance. The GNFS is more efficient than QS if $n$ is longer
      than about 116 decimal digits. This effort took 5 months.

@@

In his paper ``Circuits for integer factorisation: a proposal'' 
(\href{http://cr.yp.to/djb.html}{\texttt{http://cr.yp.to/djb.html}}),
published November 2001, D.~J.\ Bernstein \cite{Bernstein2001} 
addresses the problem of
factorising large integers. Therefore, his results are of relevance from a
RSA point of view.  As a main result Bernstein claims that the
implementation of the General Number Field Sieve algorithm (GNFS) can be
improved to factor, with the same effort as before, integers with three
times more digits.

@@

Current research results on this topic can be found at:
\vspace{-10pt}
\begin{itemize}
  \item[] \href{http://www.mersenne.org/}
               {\texttt{http://www.mersenne.org/}} \\
          \href{http://fatphil.org/maths/AKS/}
               {\texttt{http://fatphil.org/maths/AKS/}} 
\end{itemize}
\vskip +10 pt

@@

On January 18, 2002 researchers of the German University of Bonn\footnote{%
\href{http://www.ercim.org/publication/Ercim\_News/enw49/franke.html, 2002-01}
{\texttt{http://www.ercim.org/publication/Ercim\_News/enw49/franke.html, 2002-01}}}
factorised a 158-digit number into its both prime factors (these are build
with 73 and 86 decimal digits) using the GNFS method (General Number Field
Sieve).

@@

On January 18, 2002 researchers of the German University of Bonn\footnote{%
   \href{http://www.loria.fr/~zimmerma/records/rsa160}
{\texttt{http://www.loria.fr/\~{}zimmerma/records/rsa160}}} 
factorised a 160-digit number into its both prime factors (these are build
with each 80 decimal digits) using the GNFS method (General Number Field
Sieve).

>>>>

The best factorisation method known today is a further development of the
General Number Field Sieve (GNFS) \index{General Number Field Sieve (GNFS)},
which was originally devised to factor only numbers of a special form 
(like Fermat numbers).  The complexity of solving the factorisation problem
with the GNFS is asymptotically
$$
O(l) = e^{c \cdot (l \cdot \ln 2)^{1/3} \cdot  (\ln(l \cdot \ln(2))^{2/3} + o(l)}
$$
Please refer to: 
\vspace{-10pt}
\begin{itemize}{}
  \item A. Lenstra, H. Lenstra:  
          {\em The development of the Number Field Sieve} 
          \cite{Lenstra1993}.
  \item   Robert D. Silverman:  
          {\em A Cost-Based Security Analysis of Symmetric and Asymmetric
          Key Lengths} 
          \cite{Silverman2000}.
\end{itemize}

@@

\item In 1999 a 155-digit module (512 bit) was factored with an implementation
      of the General Number Field Sieve algorithm (GNFS) \index{General 
      Number Field Sieve (GNFS)}, developed by Buhler, Lenstra and Pomerance.
      The GNFS is more efficient than QS if $n$ is longer
      than about 116 decimal digits. This effort took 5 months.

@@

In his paper ``Circuits for integer factorisation: a proposal'' 
(\href{http://cr.yp.to/djb.html}{\texttt{http://cr.yp.to/djb.html}}),
published November 2001, D.~J.\ Bernstein \cite{Bernstein2001} 
addresses the problem of
factorising large integers. Therefore, his results are of relevance from a
RSA point of view.  As a main result Bernstein claims that the
implementation of the General Number Field Sieve algorithm (GNFS)
 \index{General Number Field Sieve (GNFS)} can be improved to factor, with
the same effort as before, integers with three times more digits.

@@

Current research results on this topic can be found at:
\vspace{-10pt}
\begin{itemize}
  \item[] \href{http://www.mersenne.org/}
               {\texttt{http://www.mersenne.org/}} \\
          \href{http://fatphil.org/maths/AKS/}
               {\texttt{http://fatphil.org/maths/AKS/}} Original paper in English\\
          \href{http://ls2-www.cs.uni-dortmund.de/lehre/winter200203/kt/material/primes.ps}
               {\texttt{http://ls2-www.cs.uni-dortmund.de/lehre/winter200203/kt/material/primes.ps}}\\
	       \hspace*{2em}Good explanation in German by Thomas Hofmeister. 
\end{itemize}
\vskip +10 pt

@@

On January 18, 2002 researchers of the German University of Bonn\footnote{%
\href{http://www.ercim.org/publication/Ercim\_News/enw49/franke.html, 2002-01}
{\texttt{http://www.ercim.org/publication/Ercim\_News/enw49/franke.html, 2002-01}}}
factorised a 158-digit number into its both prime factors (these are build
with 73 and 86 decimal digits) using the GNFS method (General Number Field
Sieve)\index{General Number Field Sieve (GNFS)}.

@@

On January 18, 2002 researchers of the German University of Bonn\footnote{%
   \href{http://www.loria.fr/~zimmerma/records/rsa160}
{\texttt{http://www.loria.fr/\~{}zimmerma/records/rsa160}}} 
factorised a 160-digit number into its both prime factors (these are build
with each 80 decimal digits) using the GNFS method (General Number Field
Sieve)\index{General Number Field Sieve (GNFS)}.
